# Import library

```{r}
library(tidyverse)
```

# Training dataset

## Loading the dataset

Load the training data
```{r}
training.data <- read.csv('./datasets/ml_case_training_data.csv')
training.hist.data <- read.csv('./datasets/ml_case_training_hist_data.csv')
training.output <- read.csv('./datasets/ml_case_training_output.csv')
```

## Understanding the different dataset

Check the content of the `training.data`
```{r}
head(training.data)
```

Check the shape of the `training.data` dataset
```{r}
dim(training.data)
```

Does it contain one row per client?
```{r}
training.data %>% count(id) %>% filter(n > 1)
```

We can conclude that one row correspond to an unique client.

Check the shape of the `training.hist.data` dataset
```{r}
dim(training.hist.data)
```

This dataset has more rows than the `training.data` dataset.
Let's check if a client is defined by many or only rows
```{r}
training.hist.data %>% count(id) 
```
Each client appear `12 times` here.
After the `group_by` operation, we obtain the same number of rows than the `training.data` dataset.
Let's check if the both dataset `training.data` and `training.hist.data` contains the same client
```{r}
training.hist.id <- training.hist.data %>% count(id) %>% pull(id)
training.id <- training.data$id

setdiff(training.hist.id, training.id)
rm(training.hist.id, training.id)
```

Now do the same check with the `training.output` dataset
```{r}
dim(training.output)
```

Same number of row than the `training.data` dataset
Let's check if there are identical
```{r}
setdiff(training.data$id, training.output$id)
```


We can conclude that the training dataset is about `16096` clients each defined by `40` features.


## EDA


